Towards End-user Web Scraping For Customization

### 2021-03-14 paper.tex
Incorporated PX/21 reviews

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
  Our ultimate goal is to empower end-users to customize websites in an
  intuitive and flexible way, making the web more malleable for all of
  its users.
\end{abstract}

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Thresher
\citep{hogue2005}, Sifter \citep{huynh2006} and Vegemite \citep{lin2009}
help users tweak and adapt websites to fit their unique requirements,
ranging from reorganizing or annotating content on the website to
automating common tasks. In our prior work, we presented Wildcard
\citep{litt2020a}, a customization system which enables end-users to
customize websites through direct manipulation. It does this by
augmenting websites with a table view that shows their underlying
structured data. The table is bidirectionally synchronized with the
original website, so end-users can easily customize the website by
interacting with the table, including sorting and filtering data, adding
annotations, and running computations in a spreadsheet formula language.

@@

Our key contribution is a set of three design principles that guided the
development of our system, which also offer insights that might be
applied to other end-user web scraping and customization tools
(Section~\ref{sec:design-principles}):

@@

@@

We implemented our end-user web scraping system as an addition to the
Wildcard browser extension. We start by describing our implementations
of row and column generalization, live programming, and editing by
demonstration, and then discuss some of the current limitations of our
system.

\hypertarget{generalization-algorithms}{%
\subsection{Generalization Algorithms}\label{generalization-algorithms}}

@@

At a high level, the generalization algorithm's challenge is to traverse
far enough up in the DOM tree from the demonstrated element to find the
element which corresponds to the row. We solve this using a heuristic;
the basic intuition is to find a large set of elements with similar
parallel structure. Consider the sample HTML layout in
Figure~\ref{fig:algorithm}, which displays a truncated table of
superheroes, with each row containing some nested structure:

@@

Live programming is implemented by continually running the
generalization algorithm on the DOM element under the user's cursor,
reverting if the user hovers away and committing when the user clicks.
The generated row and column selectors are used to highlight all the
matching elements on the website and create an adapter. Highlighting all
the matching column elements on the website provides visual feedback
about the system's generalization to the user. Creating an adapter
enables the system to populate the table view and set up the
bidirectional synchronization. Because the table is populated and the
bidirectional synchronization is set up, users can customize as they
scrape. Live programming is possible in our system because the
generalization algorithm and adapters execute very quickly. We have yet
to benchmark the performance in detail and compare it to other
programming-by-demonstration systems like FlashExtract \citep{le2014}
that provide live feedback.

@@

\hypertarget{generalization-algorithm}{%
\subsubsection{Generalization
Algorithm}\label{generalization-algorithm}}

@@

Below, we discuss the three design principles underlying our work and
how they relate to the broader field of end-user web scraping and
customization.

@@

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This principle
relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
end-user programming systems: users should be able to program using
familiar tools in the context where they already use their software.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-1349}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automation demonstrations. In fact, only the
demonstrations used to perform automations on the scraped website data
can be edited. If a user needs to add a new column or repair an existing
one in the scraped data table, they need to re-demonstrate the columns
and then re-run the automation script. One exception to existing editing
models worth pointing out is import.io \citep{import.io}. It allows
users to add new columns by demonstration but it is not clear whether
deleting a column and re-demonstrating it could serve the purpose of
repair.

@@

In many programming-by-demonstration web scraping systems
\citep{chasins2018, lin2009}, users only get \emph{full} feedback about
the program's execution (generalization and the scraped values) after
providing \emph{all} the demonstrations. This means they cannot adjust
their demonstrations in response to the system's feedback as they
demonstrate.

Our end-user web scraping system employs live programming techniques to
eliminate this edit-compile-debug cycle by running the generalization
algorithm and generating an adapter after each user demonstration. As we
showed in Section~\ref{sec:demos}, when a user demonstrates a value of a
column they wish to scrape, our system immediately shows how it has
generalized the user's demonstration across the other rows of the data
by highlighting the all relevant values. It also populates the table
with the scraped data based on the latest demonstration. The
highlighting and table population serve to give users a view of how
their demonstration has been generalized and what data will be available
in the table once scraped.

Many successful end-user programming systems such as spreadsheets and
SQL provide users with immediate results after entering commands. Our
live programming environment is particularly similar to that of
FlashProg \citep{mayer2015}, a framework that provides user interface
support for programming-by-demonstration systems like FlashExtract
\citep{le2014}, and relates to the idea that an important quality of
end-user programming is ``interaction with a living system''
\citep{zotero-1362}.

@@

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Because demonstrations can span
across several websites and involve complex data access automation
tasks, its interface does not provide \emph{full} live feedback about
its generalizations or the values to be scraped until all the
demonstrations have been provided and the generated program has been
run. If run on a website it has encountered before, Rousillon makes all
the previously determined generalizations visible to the user by
color-coding the values on the website that belong to the same column.
This is a desirable feature for our system as users will not have to
actively explore in order to discover which values are available for
scraping and how they are related to each other. On the extension and
repair front, Rousillon presents the web scraping code generated by
demonstration as an editable, high-level, block-based language called
Helena \citep{zotero-1349}. While Helena can be used to perform more
complex editing tasks like adding control flow, it does not support
adding or repairing columns after the demonstrations and presents a
change in the model used for creation. Our system maintains the model
used for creation by allowing users to extend and repair web scraping
code via demonstration.

@@

Like existing programming-by-demonstration approaches, web scraping in
our current implementation is limited to what can be demonstrated. This
is problematic if users want to scrape the URL associated with a link
element, which is not visible, or only scrape a substring of a value. To
solve this, we plan to harness Wildcard's formula language. End-users
will be able to use formulas targeted at web scraping to access DOM
element properties and attributes. For example, a formula like
\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
URLs of link elements. End-users will also be able to use formulas
targeted at data processing. For example, a formula like
\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
substrings of text values. Such web scraping and data processing
formulas will give end-users some of the power available to programmers
that write web scraping code in Javascript which supports a wide variety
of DOM access and processing ability.

To assess our design principles, we plan to carry out a broader
evaluation of our system through a user study. So far, we have only
tested the system amongst ourselves and a small number of colleagues.
More testing is needed to understand whether it can be successfully used
among a broader set of users across a wider variety of websites.
Furthermore, we plan to incorporate the program viewer and
disambiguation features of FlashProg \citep{mayer2015} to give users
more insight and control into the generalization process.

Our ultimate goal is to empower end-users to customize websites in an
intuitive and flexible way, and thus make the web more malleable for all
of its users.

>>>>

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
  Our ultimate goal is to empower end-users to customize websites in the
  course of their daily use in an intuitive and flexible way, and thus
  making the web more malleable for all of its users.
\end{abstract}

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Thresher
\citep{hogue2005}, Sifter \citep{huynh2006} and Vegemite \citep{lin2009}
help users to tweak and adapt websites to fit their unique requirements,
ranging from reorganizing or annotating content on the website to
automating common tasks. Millions of people also use tools like
Greasemonkey \citep{zotero-90} and Tampermonkey \citep{zotero-92} to
install browser userscripts, snippets of Javascript code which customize
the behavior of websites.

In our prior work, we presented Wildcard \citep{litt2020a}, a
customization system which enables end-users to customize websites
through direct manipulation. It does this by augmenting websites with a
table view that shows their underlying structured data. The table is
bidirectionally synchronized with the original website, so end-users can
easily customize the website by interacting with the table, including
sorting and filtering data, adding annotations, and running computations
in a spreadsheet formula language. Wildcard enables end-users to be
\emph{creators} of browser userscripts (and not just consumers) without
having to write Javascript code.

@@

We then describe the principles underlying the design of our system
(Section~\ref{sec:design-principles}):

@@

While each of these principles has been explored in prior work, our
contribution in this work is combining them into a novel application to
the domain of end user web scraping and customization.

@@

We implemented our end-user web scraping system as an addition to the
Wildcard browser extension. Prior to this work, website adapters were
manually coded in Javascript by programmers. Now, adapters can be
automatically created via demonstration. We start by describing our
implementations of \emph{wrapper induction} \citep{kushmerick2000}, live
programming, and editing by demonstration, and then discuss some of the
current limitations of our system.

\hypertarget{wrapper-induction-algorithm}{%
\subsection{Wrapper Induction
Algorithm}\label{wrapper-induction-algorithm}}

@@

At a high level, the wrapper induction algorithm's challenge is to
traverse far enough up in the DOM tree from the demonstrated element to
find the element which corresponds to the row. We solve this using a
heuristic; the basic intuition is to find a large set of elements with
similar parallel structure. Consider the sample HTML layout in
Figure~\ref{fig:algorithm}, which displays a truncated table of
superheroes, with each row containing some nested structure:

@@

The idea of ``liveness'' in programming can be traced back to Tanimoto's
work on VIVA \citep{tanimoto1990}. It generally describes programming
environments in which programmers receive immediate feedback about a
program while it is being created. In the context of Wildcard, adapters
are the program, the table interface is the output of the program and
the highlighting on the website is the visual representation of the
program. Live programming in our system is implemented by continually
re-generating an adapter based on the DOM element under the user's
cursor and the previous demonstrations if any, reverting if the user
hovers away and committing when the user clicks. The row and column
selectors generated during the wrapper induction process are used to
highlight all the matching elements on the website and create an
adapter. Highlighting all the matching column elements on the website
provides visual feedback about the system's generalization to the user.
Creating an adapter enables the system to populate the table view and
set up the bidirectional synchronization. Because the table is populated
and the bidirectional synchronization is set up, users can customize as
they scrape. Live programming is possible in our system because the
wrapper induction algorithm and adapters execute very quickly. We have
yet to benchmark the performance in detail and compare it to other
end-user web scraping systems like FlashProg \citep{mayer2015} that
offer live programming environments.

@@

Since our system is still under development, it has a variety of
limitations. In this section we describe two of the most notable ones.

\hypertarget{wrapper-induction-algorithm-1}{%
\subsubsection{Wrapper Induction
Algorithm}\label{wrapper-induction-algorithm-1}}

@@

Below, we describe our use of three existing design principles in a
novel way for the domains of end-user web scraping and customization.

@@

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This principle
relates to the idea of ``in-place toolchains'' \citep{zotero-60} for
end-user programming systems: users should be able to program using
familiar tools in the context where they already use their software.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automation demonstrations. In fact, only the
demonstrations used to perform automations on the scraped website data
can be edited. If a user needs to add a new column or repair an existing
one in the scraped data table, they need to re-demonstrate the columns
and then re-run the automation script. One exception to existing editing
models worth pointing out is import.io \citep{import.io}. It allows
users to add new columns by demonstration but it is not clear whether
deleting a column and re-demonstrating it could serve the purpose of
repair.

@@

In many programming-by-demonstration web scraping systems
\citep{chasins2018, lin2009}, users only get \emph{full} feedback about
the program's execution (result of wrapper induction and the scraped
values) after providing \emph{all} the demonstrations. This means they
cannot adjust their demonstrations in response to the system's feedback
as they demonstrate.

Our end-user web scraping system provides level 3 liveness under
Tanimoto's liveness hierarchy \citep{tanimoto1990}. Level 3 liveness
describes a system that is constantly listening for actions from the
user, automatically re-constructing and re-executing the program
whenever one happens instead of requiring an explicit command from the
user. To eliminate the described edit-compile-debug cycle, our system
automatically runs the wrapper induction algorithm and generates an
adapter after each user demonstration. As we showed in
Section~\ref{sec:demos}, when a user demonstrates a value of a column
they wish to scrape, our system immediately shows how it has generalized
the user's demonstration across the other rows of the data by
highlighting the all relevant values on the website. It also populates
the table with the scraped data based on the latest demonstration. The
highlighting and table population serve to provide a visual
representation of the adapter's execution.

Many successful end-user programming systems such as spreadsheets and
SQL provide users with immediate results after entering commands. Our
live programming environment is particularly similar to that of
FlashProg \citep{mayer2015}, a framework that provides user interface
support for programming-by-demonstration systems like FlashExtract
\citep{le2014}, and relates to the idea that an important quality of
end-user programming is ``interaction with a living system''
\citep{zotero-60}.

@@

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Because demonstrations can span
across several websites and involve complex data access automation
tasks, its interface does not provide \emph{full} live feedback about
its generalizations or the values to be scraped until all the
demonstrations have been provided and the generated program has been
run. If run on a website it has encountered before, Rousillon makes all
the previously determined generalizations visible to the user by
color-coding the values on the website that belong to the same column.
This is a desirable feature for our system as users will not have to
actively explore in order to discover which values are available for
scraping and how they are related to each other. On the extension and
repair front, Rousillon presents the web scraping code generated by
demonstration as an editable, high-level, block-based language called
Helena \citep{zotero-51}. While Helena can be used to perform more
complex editing tasks like adding control flow, it does not support
adding or repairing columns after the demonstrations and presents a
change in the model used for creation. Our system maintains the model
used for creation by allowing users to extend and repair web scraping
code via demonstration.

@@

Like existing programming-by-demonstration approaches, web scraping in
our current implementation is limited to what can be demonstrated by
point-and-click. More generally, this surfaces a fundamental limitation
of programming-by-demonstration: the inability to specify logic. One
solution for this is taking advantage of spreadsheet formulas which have
enabled millions of end-users to specify logic. Because of this,
Wildcard already includes a spreadsheet-like formula language for
specifying customizations. We plan to extend this language to augment
our demonstration-based web scraping with the goal of raising the
ceiling on the expressiveness available to end-users. One concrete use
case for this is scraping DOM element attributes which cannot be
demonstrated by point-and-click but contain valuable data. For example,
link elements have an \emph{href} attribute which contain the URLs
associated with the link element and video elements have
\emph{currentTime} and \emph{duration} attributes which contain data
about the current playback position and duration respectively. This use
of spreadsheet-like formulas to specify logic is related to approaches
taken by Microsoft Power Apps \citep{zotero-94}, Glide
\citep{zotero-108}, Coda \citep{zotero-110} and Gneiss
\citep{chang2014}.

To assess our design principles, we plan to carry out a broader
evaluation of our system through a user study. So far, we have only
tested the system amongst ourselves and a small number of colleagues.
More testing is needed to understand whether it can be successfully used
among a broader set of users across a wider variety of websites. We also
plan to provide more insight, feedback and control into the wrapper
induction process. This is particularly important when the system
produces an error or is not able to generate an adapter for a website.
One solution for this would be to incorporate a version of the program
viewer and disambiguation features of FlashProg \citep{mayer2015}.
Wrangler \citep{kandel2011}, whose interface is also centered around a
table representation, could also provide some inspiration.

Our ultimate goal is to empower end-users to customize websites in the
course of their daily use in an intuitive and flexible way, and thus
make the web more malleable for all of its users.
